### 2012-12-13 inst/examples/may79-example.Rmd
clear example where GP performs nearly optimally while ricker dynamics in place of BH perform poorly.

```{r}
f <- May
p <- c(r = .75, k = 10, a=1.3, H=1, Q = 3)
K <- 8 # approx
```

@@

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.6
x <- numeric(T)
x[1] <- 1
```

@@

Noise function, profit function
```{r}
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
#profit <- profit_harvest(1,0,0)

profit = function(x,h) pmin(x, h)
```

@@

```{r}
x[1] = 2.5
for(t in 1:(T-1))
  x[t+1] = z_g(sigma_g) * f(x[t], h=0, p=p)
plot(x)
```

@@

qplot(x_grid, xt1[1,])
```

@@

yt10 <- yt1
for(s in 1:10)
  yt10 <- yt10 %*% F_true
qplot(x_grid, yt10[1,])
```

@@

```{r}
matrices_gp <- gp_transition_matrix(Ef, V, x_grid, h_grid)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

@@

```{r}
matrices_estimated <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g=0.01)
opt_estimated <- find_dp_optim(matrices_estimated, x_grid, h_grid, 20, 0, profit, delta=.01)
```

>>>>

```{r}
f <- May
p <- c(r = .75, k = 10, a=1.5, H=1, Q = 3)
K <- 7.5 # approx
```

@@

```{r}
x_grid <- seq(0, 1.5 * K, length=101)
sigma_g <- 0.3
delta <- 0.01
OptTime = 20
reward = numeric(length(x_grid))
xT = x_grid[4]
reward = profit(x_grid[101],x_grid[101]) + 1/(1-delta)^OptTime # reward for more than 
```

@@

Noise function, profit function
```{r}
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
#profit <- profit_harvest(1,0,0)
profit = function(x,h) pmin(x, h)
```

@@

```{r}
Tobs <- 100
x <- numeric(Tobs)
x[1] <- K
for(t in 1:(Tobs-1))
  x[t+1] = z_g(sigma_g) * f(x[t], h=0, p=p)
plot(x)
```

Very crude estimate of parameter values

```{r}
K = mean(x)
r = 0.5 * sigma_g^2 / var

#cor <- acf(x)$acf[,,1]
#m <- which(cor < 0)[1] - 1
#l <- lm(y ~ x, data=data.frame(x = 1:6, y = log(cor[1:6])))
#r <- - as.numeric(l$coefficients[2] / 2)

f_alt <- Ricker
p_alt <- p
```

@@

qplot(x_grid, xt10[1,]) + geom_point(aes(y=xt1[1,]), col="grey")

```

@@

yt10 <- yt1
for(s in 1:20)
  yt10 <- yt10 %*% F_true
qplot(x_grid, yt10[1,]) + geom_point(aes(y=yt1[1,]), col="grey")
```

@@

```{r}
matrices_gp <- gp_transition_matrix(Ef, V, x_grid, h_grid)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, OptTime, xT, profit, delta, reward=1e6)
```

@@

```{r}
matrices_estimated <- f_transition_matrix(f_alt, p_alt, x_grid, h_grid, sigma_g)
opt_estimated <- find_dp_optim(matrices_estimated, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

### 2012-12-13 inst/examples/reed-example.Rmd
clear example where GP performs nearly optimally while ricker dynamics in place of BH perform poorly.

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
require(tgp)
library(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
K = mean(x)
r = 0.5 * sigma_g^2 / var(x)

>>>>

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
library(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
K = mean(x)
r = 0.5 * sigma_g^2 / var
